### 2017-03-02 case/tx.tex
xbox and conclusion
all-in-one

\begin{figure*}[t!]
  \centering
  \begin{subfigure}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{./figures/scripts/MutationDUTJaccard3DFigure_0_10.pdf}
    % \caption{$Pr_{ed} \in [0.05, 0.1, 0.15]$}
    \caption{$0.05 \le Pr_{ed} \le 0.15$}
  \end{subfigure}\hspace*{0.01\textwidth}
  \begin{subfigure}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{./figures/scripts/MutationDUTJaccard3DFigure_0_30.pdf}
    \caption{$0.2 \le Pr_{ed} \le 0.35$}
  \end{subfigure}\hspace*{0.01\textwidth}
  \begin{subfigure}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{./figures/scripts/MutationDUTJaccard3DFigure_0_50.pdf}
    \caption{$0.4 \le Pr_{ed} \le 0.5$}
  \end{subfigure}\hspace*{0.01\textwidth}
  \caption{\textbf{Jaccard Distance Between Mutation and DUT Traces.} For each
  data point, the mean of the 5 runs is used.}
  \label{fig:mutation_dut}
\end{figure*}

@@

\begin{figure*}[t!]
  \centering
  \begin{subfigure}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{./figures/scripts/StepCount3DFigure_0_10.pdf}
    \caption{$Pr_{ed} \in [0.05, 0.10, 0.15]$}
  \end{subfigure}\hspace*{0.01\textwidth}
  \begin{subfigure}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{./figures/scripts/StepCount3DFigure_0_30.pdf}
    \caption{$Pr_{ed} \in [0.2, 0.25, 0.3, 0.35]$}
  \end{subfigure}\hspace*{0.01\textwidth}
  \begin{subfigure}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{./figures/scripts/StepCount3DFigure_0_50.pdf}
    \caption{$Pr_{ed} \in [0.40, 0.45, 0.50]$}
  \end{subfigure}
  \caption{\textbf{Average Searching Step Per Packet.} For each data point, the mean of 5 runs
  is used.}
  \label{fig:cost}
\end{figure*}

Fig.~\ref{fig:cost} shows the distribution of ASSPP at different $Pr_{ed}$.
Similar to the case in Fig.~\ref{fig:mutation_dut}, $Pr_{ds}$ plays a dominant
role in determine the searching cost. One interesting observation is that the
search cost peaks when $Pr_{ds}$ is high while $Pr_{es}$ is low. In such loss
probability combinations, sniffer misses many data packets from the DUT but
picks up lots of \textit{dangling} $Ack$ packets from the DUT. Because the $Ack$
packet has neither sequence numbers nor retry flag, the searching algorithm had
a hard time resolving such uncertainty.

@@

\begin{figure}[t!]
  \centering
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{./figures/scripts/PrecisionFigure.pdf}
  \end{subfigure}
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{./figures/scripts/RecallFigure.pdf}
  \end{subfigure}
  \caption{\textbf{Precision and Recall of Validation Results.}}
  \label{fig:precision}
\end{figure}

>>>>

\begin{figure*}[t!]
  \centering
  \begin{subfigure}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{MutationDUTJaccard3DFigure_0_10.pdf}
    % \caption{$Pr_{ed} \in [0.05, 0.1, 0.15]$}
    \caption{$0.05 \le Pr_{ed} \le 0.15$}
  \end{subfigure}\hspace*{0.01\textwidth}
  \begin{subfigure}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{MutationDUTJaccard3DFigure_0_30.pdf}
    \caption{$0.2 \le Pr_{ed} \le 0.35$}
  \end{subfigure}\hspace*{0.01\textwidth}
  \begin{subfigure}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{MutationDUTJaccard3DFigure_0_50.pdf}
    \caption{$0.4 \le Pr_{ed} \le 0.5$}
  \end{subfigure}\hspace*{0.01\textwidth}
  \caption{\textbf{Jaccard Distance Between Mutation and DUT Traces.} For each
  data point, the mean of the 5 runs is used.}
  \label{fig:mutation_dut}
\end{figure*}

@@

\begin{figure*}[t!]
  \centering
  \begin{subfigure}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{StepCount3DFigure_0_10.pdf}
    \caption{$Pr_{ed} \in [0.05, 0.10, 0.15]$}
  \end{subfigure}\hspace*{0.01\textwidth}
  \begin{subfigure}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{StepCount3DFigure_0_30.pdf}
    \caption{$Pr_{ed} \in [0.2, 0.25, 0.3, 0.35]$}
  \end{subfigure}\hspace*{0.01\textwidth}
  \begin{subfigure}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{StepCount3DFigure_0_50.pdf}
    \caption{$Pr_{ed} \in [0.40, 0.45, 0.50]$}
  \end{subfigure}
  \caption{\textbf{Average Searching Step Per Packet.} For each data point, the mean of 5 runs
  is used.}
  \label{fig:cost}
\end{figure*}

Fig.~\ref{fig:cost} shows the distribution of ASSPP at different $Pr_{ed}$.
Similar to the case in Fig.~\ref{fig:mutation_dut}, $Pr_{ds}$ plays a dominant
role in determine the searching cost. One interesting observation for this
particular protocol is that the
search cost peaks when $Pr_{ds}$ is high while $Pr_{es}$ is low. In such loss
probability combinations, sniffer misses many data packets from the DUT but
picks up lots of \textit{dangling} $Ack$ packets from the DUT. Because the $Ack$
packet has neither sequence numbers nor retry flag, the searching algorithm had
a hard time resolving such uncertainty.

@@

\begin{figure}[t!]
  \centering
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{PrecisionFigure.pdf}
  \end{subfigure}
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{RecallFigure.pdf}
  \end{subfigure}
  \caption{\textbf{Precision and Recall of Validation Results.}}
  \label{fig:precision}
\end{figure}
